### 2017-06-30 draft/unique-linear.tex
snapshot

\begin{mathpar}
  \inferrule{
    A = A_1 \OVERRIDE \dots \OVERRIDE A_n \\
    A_i \vdash e_i : t_i 
  }{
    A \vdash \REC{ \overline{a_i=e_i}} : \REC{ \overline{a_i :^{P_i} t_i}}
  }

@@

  \inferrule{
    A_0, x:t \vdash e : t' \\
    A = A_0^*
  }{
    A \vdash \LAM x t e : (t \to t')
  }
\end{mathpar}
Function closures have ``infinite'' splitting $(a :^P t)^*$ into $(a :^Q t)$.
\begin{itemize}
\item $P \le \{\READ\}$ propagate $Q = \READ$, no action required
\item $\WRITE \in P$: propagate $Q = \READ$, insert copy into closure
\end{itemize}

Function application has no particular restrictions, it seems.
\begin{mathpar}
  \inferrule{
    A_0 \vdash e_0 : (t_1 \to t_2) \\
    A_1 \vdash e_1 : t_1 \\
    A = A_0 \OVERRIDE A_1
  }{
    A \vdash \APP{e_0}e_1 : t_2
  }
\end{mathpar}

Look at combining $a :^O t \OVERRIDE a:^P t$ upwards to $a : ^Q t$
\begin{itemize}
\item if $O=\emptyset$ or $P=\emptyset$ (field only used in one branch), then $Q = O \cup P$, no
  action required
\item if $O\subseteq \{\READ\}$: $Q = O \cup P$,
  no further action required as potential writing in $P$ happens after reading
\item if $\WRITE \in O$, $P = \{\READ\}$: two choices, not clear
  which is better
  \begin{itemize}
  \item $Q = \READ$ insert copy, propagate left to the write operation
  \item $Q = \WRITE$ insert copy, propagate right to the read operation
  \end{itemize}
\item if $\WRITE\in O$, $\WRITE \in P$: $Q = \WRITE$ insert copy,
  propagate left (or right)
\end{itemize}

\begin{mathpar}
  \inferrule
  { A_1 \vdash e_1 : t_1 \\
    A_2, x : t_1 \vdash e_2 : t_2 \\
    A = A_1 \OVERRIDE A_2
  }
  { A \vdash \LET x{e_1} e_2 : t}
\end{mathpar}

>>>>

Effects attached to single record labels
\begin{align*}
  P, Q &\subseteq \{ \READ, \WRITE \}
\end{align*}

\begin{figure}[tp]
  \begin{mathpar}
    \inferrule{
      A = A_1 \OVERRIDE \dots \OVERRIDE A_n \\
      A_i \vdash e_i : t_i }{ A \vdash \REC{ \overline{a_i=e_i}} :
      \REC{ \overline{a_i :^{P_i} t_i}} }

@@

    \inferrule{
      A_0, x:t \vdash e : t' \\
      A = A_0^* }{ A \vdash \LAM x t e : (t \to t') }

  \inferrule{
    A_0 \vdash e_0 : (t_1 \to t_2) \\
    A_1 \vdash e_1 : t_1 \\
    A = A_0 \OVERRIDE A_1
  }{
    A \vdash \APP{e_0}e_1 : t_2
  }

  \inferrule
  { A_1 \vdash e_1 : t_1 \\
    A_2, x : t_1 \vdash e_2 : t_2 \\
    A = A_1 \OVERRIDE A_2
  }
  { A \vdash \LET x{e_1} e_2 : t}
  \end{mathpar}
  \caption{Propagation rules}
  \label{fig:field-effects}
\end{figure}
Function closures have ``infinite'' splitting $(a :^P t)^*$ into $(a :^Q t)$.
\begin{itemize}
\item $P \subseteq \{\READ\}$ propagate $Q = \READ$, no action required
\item $\WRITE \in P$: propagate $Q = \READ$, insert copy into closure
\end{itemize}

Function application has no particular restrictions, it seems.
Let improves on lambda combined with app because infinite splitting is avoided.

Look at combining $a :^O t \OVERRIDE a:^P t$ upwards to $a : ^Q t$:
$Q= O \OVERRIDE P$
\begin{itemize}
\item if $O=\emptyset$ or $P=\emptyset$ (field only used in one branch), then $Q = O \cup P$, no
  action required
\item if $O\subseteq \{\READ\}$: $Q = O \cup P$,
  no further action required as potential writing in $P$ happens after reading
\item if $\WRITE \in O$, $P = \{\READ\}$: two choices, not clear
  which is better
  \begin{itemize}
  \item $Q = \READ$ insert copy, propagate left to the write operation
  \item $Q = \WRITE$ insert copy, propagate right to the read operation
  \end{itemize}
\item if $\WRITE\in O$, $\WRITE \in P$: $Q = \WRITE$ insert copy,
  propagate left (or right)
\end{itemize}

Combining environments: pointwise

Combining records
\begin{mathpar}
  \inferrule
  {}
  {
    \REC{ {a :^{Q_a} t_a}, {b :^{Q_b} t_b}}
    =
    \REC{ {a :^{O_a} t_a}, {b :^{O_b} t_b}}
    \OVERRIDE
    \REC{ {a :^{P_a} t_a}, {b :^{P_b} t_b}}
  }
\end{mathpar}

\clearpage
\begin{mathpar}
  \begin{array}{|c|c||c|c||c|c|l}
    Q_a&Q_b&O_a&O_b&P_a&P_b& \\
    \hline
    P_a &\emptyset& \emptyset & \emptyset & P_a & \emptyset & \\
    O_a & \emptyset& O_a & \emptyset & \emptyset & \emptyset & \\
    P_a\cup\READ   &\emptyset& \subseteq\READ & \emptyset & P_a & \emptyset & \\
    \READ&\READ& \WRITE\in & \emptyset & \READ & \emptyset
                       &  \text{copy, propagate left to write}\\
    \WRITE &\READ& \WRITE\in & \emptyset & \WRITE\in & \emptyset
                       &\text{copy, propagate left to write} \\
  \end{array}

  \begin{array}{|c|c||c|c||c|c|l}
    Q_a&Q_b&O_a&O_b&P_a&P_b& \\
    \hline
    P_a & P_b & \emptyset & \emptyset & P_a & P_b & \\
    O_a & P_b & O_a & \emptyset & \emptyset & P_b & \\
    P_a\cup\READ   &P_b& \subseteq\READ & \emptyset & P_a & P_b & \\
    \READ&P_b\cup\READ& \WRITE\in & \emptyset & \READ & P_b
                       &  \text{copy, propagate left to write}\\
    \WRITE & P_b\cup\READ & \WRITE\in & \emptyset & \WRITE\in & P_b
                       &\text{copy, propagate left to write} \\
  \end{array}

  \begin{array}{|c|c||c|c||c|c|l}
    Q_a&Q_b&O_a&O_b&P_a&P_b& \\
    \hline
    P_a & O_b & \emptyset & O_b & P_a & \emptyset & \\
    O_a & O_b & O_a & O_b & \emptyset & \emptyset & \\
    P_a\cup\READ  & O_b & \subseteq\READ & O_b & P_a & \emptyset & \\
    \READ&O_b \cup\READ& \WRITE\in & O_b & \READ & \emptyset
                       &  \text{copy, propagate left to write}\\
    \WRITE &O_b\cup\READ& \WRITE\in & O_b & \WRITE\in & \emptyset
                           &\text{copy, propagate left to write} \\
  \end{array}

\begin{array}{|c|c||c|c||c|c|l}
    Q_a&Q_b&O_a&O_b&P_a&P_b& \\
    \hline
    P_a &\emptyset& \emptyset & \emptyset & P_a & \emptyset & \\
    O_a & \emptyset& O_a & \emptyset & \emptyset & \emptyset & \\
    P_a\cup\READ   &\emptyset& \subseteq\READ & \emptyset & P_a & \emptyset & \\
    \READ&\READ& \WRITE\in & \emptyset & \READ & \emptyset
                       &  \text{copy, propagate left to write}\\
    \WRITE &\READ& \WRITE\in & \emptyset & \WRITE\in & \emptyset
                       &\text{copy, propagate left to write} \\
  \end{array}
\end{mathpar}
